Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-21 ApproximateCode.tex
version 4.0

% !TEX TS-program = pdflatex
\documentclass[sigconf]{acmart}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{subfigure}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subfigure}

\renewcommand{\algorithmicrequire}{\textbf{Input:}} % Use Input in the format of Algorithm
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm

@@

\author{Huayi Jin}

%-------------------------ATTANTION-------------------------%
%                                                           %
% orange words show the content that requires to be add     %
% blue words need to be perfected or changed                %
% gray words are the placeholder which is easy to fill      %
%                                                           %
%-----------------------------------------------------------%

@@

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for video applications in cloud storage systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
\end{abstract}

@@

With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
Therefore, in this paper, we set out to answer the following question,
\textbf{In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?}

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance would be sacrificed.
Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}. However, the compression and decompression process results in very large computational overhead, high recovery speed and high response time, which is not suitable for video applications.
Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.

To address the above problem, in this paper, we propose Approximate Code\footnote{This article abbreviates ``Approximate'' to ``Appr. '' when necessary.}, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems. The key idea of Approximate Code is treating the important/unimportant data in different ways. For important data, we add additional parities to provide high capability of fault tolerance. On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery. When triple disks fail, the lost data can be reconstructed via a fuzzy manner.

We have the following contributions of this work,
\begin{enumerate}
\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
\item Approximate Code can be implemented by combining most erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
\end{enumerate}

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|c|l|}
\hline
Symbols & Description \\ \hline
$k$ & the number of data nodes in an array \\ \hline
$r$ & the number of local parity nodes in an array \\ \hline
$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
$h$ & the number of arrays \\ \hline
$g$ & the number of global parity nodes \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline 
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data \\ \hline
UD & unimportant data \\ \hline
\end{tabular}
\end{table}

\subsection{Basis of Video Storage}\label{video storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy algorithms before storage.

\subsubsection{Video coding}
H.264 is one of the advanced algorithms for this type of work. This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor. For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.

H.264 classifies all frames into three different categories:
\begin{enumerate}
    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
\end{enumerate}
A GOP consists of multiple consecutive I, P, and B frames that are independent of frames in other GOPs to prevent bit error spread.
%In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}. 
Therefore, within each GOP, the I frame has the highest importance because other frames rely on it for recovery; the importance of the P frame is second, and the B frame has the least importance. Based on this feature, a special program can be designed to distinguish the importance of video frames.

\iffalse
\begin{figure}[]
\centering
\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}
\fi

\subsubsection{Video Frame Recovery}
In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete. However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques. One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context}.

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.This is a technique that can model natural motion within a video, and generate frames according to this modelling.

In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow. Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses as well as a context-aware Synthesis approach\cite{niklaus2018context} have so far produced the new state-of-the-art results in terms of PSNR and middlebury benchmark respectively.

@@

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, RL-code \cite{RL}, and so on. Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.

Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating. Several attempts have been made to address this issue. Local Construction Code (LRC) \cite{LRC} is one of these attempts which succeeds in reducing the bandwidth and I/Os required for repair reads at the expense of higher storage overhead.

Unlike the RS code basing on additions and multiplications, another type of erasure codes is XOR-based codes and some are used in RAID (Redundant Arrays of Independent Drives) structures. This type of codes uses purely XOR operations, therefore showing a great advantage on encoding/decoding speed. XOR-based codes like EVENODD \cite{EVENODD} and H-code \cite{hcode} can tolerate 2 disk failures (EVENODD can even be designed to tolerate 3 disk failure), and they can be directly applied in RAID structures. More sophisticated ones like STAR code \cite{STAR} and TIP code \cite{tip} can tolerate 3 disk failures.

STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code. It employs a novice diagonal redundancy as shown in Figure \ref{fig:star-enc}.
\begin{figure}[!ht]
 \centering
 \subfigure[Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-hori.pdf}
 }
 \hspace{5pt}
 \subfigure[Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-diag.pdf}
 } \\
 \subfigure[Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
  \includegraphics[width=0.20\textwidth]{photo/star-anti.pdf}
 }
 \hspace{5pt}
 \caption{Encoding of STAR code ($p = 5$).}
 \label{fig:star-enc}
\end{figure}

TIP-code \cite{tip} is a solution for p or p+1 disks, where p is a prime number. Compared to STAR, Tip's input of the diagonal and anti-diagonal parity is modified so they are evenly distributed among all the data blocks. This minor modification has enabled TIP-code to achieve optimal update complexity.

@@

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced. 
Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code.}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Appr.  Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr. \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

\subsection{Our Motivation}
Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.

First, the overhead of existing 3DFTs erasure codes is too high.
Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.

@@

\subsection{Overview of Approximate Code Framework}
The Approximate Code mainly includes three operations: code segmentation, structure selection and code generation. We use Figure \ref{fig-framework} to illustrate our design.

\subsubsection{Code Segmentation}
For an input erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parity block into two parts: local and global. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

In the example, a 3DFTs erasure code with 4 data chunks and 3 parity chunks is input, and its 3 parity chunks are separated into two local and one global parity chunks.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the structure for the input erasure code.
There are two main structures that distribute important and unimportant data in different ways.
As shown in Figure \ref{fig-framework}, in \emph{Structure I}, important data occupies 1 block in each node, and in \emph{Structure II}, it occupies 1 data arrays.
We specify that in \emph{Structure I}, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both \emph{Structure I} and \emph{Structure II} just fills up $k$ nodes.

Since \emph{Structure I} distributes important data across each node, it guarantees a more balanced load. \emph{Structure II} concentrates important data into an array, and provides greater reliability for important data. A detailed analysis of this will be presented in Section +\ref{ReconstructionFT}.

\subsubsection{Code Generation}\label{code-gen}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.

The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and $Structure$. 
We define the naming rules of the output Approximate Code as \textbf{``Approximate XXX Code ($k,r,g,h, Structure$)''}, where ``XXX'' is the name of input erasure code. Paremeter $Structure$ is I or II and it can be omitted when not focusing on the specific construction.

In a $n$-node array, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ arrays, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes in Approximate Code ($k,r,g,h$) is 
$h*(k+r) + g$.

Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually set to 1 or 2.

\iffalse
\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure I}, and Approximate Code $(3,1,3)$ in \emph{Structure II}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-RS-43.pdf}
\caption{The generate matrix of RS-based Approximate Codes $(4,1,4)$, where $ID_i$ and $UD_i$ represent the important and unimportant data in $N_i$. $G_0$ and $G_1$ are the parity blocks corresponding to important data blocks.}
\label{fig-ap-rs}
\end{figure}
\fi

\subsection{Approximate RS Code}
For RS(k,p), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$. RS also supports both two structures.

For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS(4,3). It is divided into two local parities and one global parities with the \emph{Structure II} and it generate Approximate RS Code (4,2,1,3,II).
As a result, the unimportant data constitutes RS(4,2), and the important data constitutes RS(4,3).

>>>>

\documentclass[sigconf]{acmart}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{subfigure}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{array}

@@

\author{Huayi Jin}
\email{keplar_gd@sjtu.edu.cn}
\affiliation{%
  \institution{Shanghai Jiao Tong University}
}

\author{Chentao Wu}

\author{Xin Xie}

\author{Jie Li}

\author{Minyi Guo}

\author{Xubin He}
\affiliation{%
  \institution{}
}

\author{Yuanyuan Dong}
\author{Hao Lin}
\author{Jianfeng Zhang}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{The Alibaba Group}
}

@@

To address this problem, in this paper, we propose Approximate Code, which is an erasure coding framework for tiered video storage in cloud systems. The key idea of Approximate Code is distinguishing the important data and unimportant data in videos with different capabilities of fault tolerance. On one hand, for important data, Approximate Code provides triple parities to provide high reliability. On the other hand, single/double parities are applied for unimportant data, which can save the storage cost and accelerate the recovery process. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop systems. The results show that, compared to traditional 3DFTs using various erasure codes such as RS, STAR and TIP-Code, Approximate Code reduces the number of parities by up to 55\%, saves the storage cost by up to 20.8\%, increase the recovery speed by up to 1.25X when single disk fails, and can reconstruct the whole video data via fuzzification when triple disks fail.
\end{abstract}

\ccsdesc[500]{Information systems~Distributed storage}
\ccsdesc[500]{Computer systems organization~Dependable and fault-tolerant systems and networks}

@@

With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
Therefore, in this paper, we set out to answer the following question:

\textbf{In a cloud storage system, how to efficiently store tremendous video data in 3DFTs?}

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
Another solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.} is also a common strategy for reducing storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}.
\textcolor{red}{However, the compression and decompression processes result in a large amount of computational overhead, which decreases their efficiency in frequent failure scenarios like cloud.}
Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.

To address the above problem, in this paper, we propose Approximate Code, which is an erasure coding framework to provide comprehensive solution for video data storage in cloud systems. The key idea of Approximate Code is treating the important/unimportant data in different ways. For important data, we add additional parities to provide high capability of fault tolerance. On the other hand, the unimportant data are encoded with a minimum number of parities, which only supply the basic requirement of the recovery. When triple disks fail, the lost data can be reconstructed via a fuzzy manner.

We have the following contributions of this work,
\begin{enumerate}
\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
\end{enumerate}

@@

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering\small
\begin{tabular}{|p{1cm}<{\centering}|p{6.5cm}|}
\hline \hline
Symbols & \multicolumn{1}{c|}{Description} \\ \hline
$k$ & the number of data nodes in a local stripe \\ \hline
$r$ & the number of local parity nodes in a local stripe \\ \hline
$n$ & the number of all data and parity nodes in a local stripe ($n=k+r$) \\ \hline
$h$ & the number of local stripes to construct a global stripe \\ \hline
$g$ & the number of global parity nodes \\ \hline
$N$ & total number of all nodes ($N=(k+r)h+g$) \\ \hline
$E_{i,j}$ & element at the $i$-th row and $j$-th column \\ \hline
$D_i$ & data nodes \\ \hline
$P_{I}$ & the mathematical expectation of important data being recoverable under faults that exceed fault tolerance \\ \hline
$P_{U}$ & the mathematical expectation of unimportant data being recoverable under faults that exceed fault tolerance \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data in a video file \\ \hline
UD & unimportant data in a video file \\ \hline
\end{tabular}
\end{table}

\subsection{Basis of Video Storage}\label{video storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy compression algorithms before storage.

\subsubsection{Video coding}
H.264 \cite{wiegand2003overview} is one of the advanced algorithms. This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor. For a normal HD video file metioned as above, H.264 can reduce its size by about 10 times, only 443.27MB.

H.264 classifies all frames into three different categories:
\begin{enumerate}
    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
\end{enumerate}
A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames that are independent of the frames in other GOPs to prevent bit error spread, as shown in Figure \ref{H264-IPB}.
%In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}. 
Therefore, within each GOP, the I frame has the highest importance because other frames rely on it for recovery; the importance of the P frame is second, and the B frame has the least importance. Based on this feature, a special program can be designed to distinguish the importance of video frames.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}

\subsubsection{Video Frame Recovery}
In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete. However, the lost frames can still be recoverable with the benefit of nowadays powerful deep learning techniques. One of them is named video frame interpolation \cite{meyer2015phase, niklaus2018context}.

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones. This is a technique that can model natural motion within a video, and generate frames according to the model.

In deep learning methods, optical changes between the frames are trained in a supervised setup mapping two frames to their ground truth optical flow. Among all these, a multi-scale network\cite{van2017frame} based on recent advances in spatial transformers and composite perceptual losses has so far produced the new state-of-the-art results in terms of PSNR, and so has a context-aware Synthesis approach\cite{niklaus2018context} in terms of middlebury benchmark.

@@

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes \cite{RS}, Cauchy-RS codes \cite{CRS}, STAR code \cite{STAR}, Triple-Star code \cite{TripleStar}, Triple-Parity code \cite{TPtech}, HDD1 code \cite{HDD}, RSL-code \cite{RSL}, RL-code \cite{RL}, and so on. Typical non-MDS codes contain WEAVER codes \cite{WEAVER}, HoVercodes \cite{HoVer}, T-code \cite{TCode}, HDD2 code \cite{HDD}, Pyramid codes \cite{Pyramid}, Local Reconstruction Codes \cite{LRC}, Locally Repairable Codes \cite{XORing}, etc.
In the following we mainly introduce the classic erasure codes used in this paper.

Reed Solomon Code \cite{RS} (RS code) is one kind of classic MDS codes, but its scheme requires additions and multiplications over finite fields and results in high complexity in decoding and updating. Several attempts have been made to address this issue.

\textcolor{red}{Need to update}
Local Construction Code (LRC) \cite{LRC} divides the data nodes into multiple local groups, each with a local parity node, and the global parity is calculated by all data nodes. Therefore, when a single node is corrupted, data can be recovered by local parity without requiring access to all nodes.
LRC reduce the bandwidth and I/Os required for repair reads at the expense of higher storage overhead, as shown in Figure \ref{LRC}.

\begin{figure}
    \centering
    \includegraphics[height=2.5cm]{photo/LRC.pdf}
    \caption{LRC}
\end{figure}

STAR code \cite{STAR} is an extension of the double-erasure-correcting EVENODD \cite{EVENODD} code, and a modification of the generalized triple-erasure-correcting EVENODD code. It employs a novice diagonal redundancy as shown in the left of Figure \ref{fig-star-tip}.

In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $E_{0,5} = E_{0,0} \oplus E_{0,1} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Horizontal parity coding (e.g., $E_{0,7} = E_{0,0} \oplus E_{0,2} \oplus E_{0,3} \oplus E_{0,4} \oplus E_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}

\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = E_{3,1} \oplus E_{2,2} \oplus E_{1,3} \oplus E_{0,4}$ and $E_{0,6} = E_{0,0} \oplus E_{3,2} \oplus E_{2,3} \oplus E_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Diagonal parity coding (e.g., $E_{0,1} = E_{0,0} \oplus E_{5,2} \oplus E_{4,3} \oplus E_{2,5} \oplus E_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}

\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = E_{0,1} \oplus E_{1,2} \oplus E_{2,3} \oplus E_{3,4}$ and $E_{0,7} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP Code:} Anti-diagonal parity coding (e.g., $E_{0,6} = E_{0,0} \oplus E_{1,1} \oplus E_{2,2} \oplus E_{4,4} \oplus E_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}
\caption{Encoding of STAR (subfigure (a),(c) and (e)) and TIP (subfigure (b),(d) and (f)) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
\label{fig-star-tip}
\end{figure}

TIP code is also an XOR-based 3DFTs erasure code.
Compared with STAR code, the encoding and data arrangement of TIP code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.

STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.

@@

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced. 
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

\begin{table}[ht]
\centering 
\caption{
\textcolor{red}{Need to update}
Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
\small
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Approximate Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate \\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

\subsection{Our Motivation}

%Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons. 
%First, the overhead of existing 3DFTs erasure codes is too high.
Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

From the summary of Table \ref{tab-AS-EC-AP}, we can find that existing solutions have high storage cost for video storage. Although approximate storage achieves low cost, the reliability cannot be satisfied in cloud environment. A feasible solution is combining the existing solutions together with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.

@@

\subsection{Overview of Approximate Code Framework}
The Approximate Code framework contains four main steps, code input, code segementation, structure selection and code generation, as shown in Figure \ref{fig-framework}.

\subsubsection{Code Input}
Acquire an erasure coding input and get the corresponding parameters. Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted by Approximate Code. Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.

\subsubsection{Code Segmentation}
For an inputted erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parities into two parts: local and global parities. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

For example, several erasure codes in 3DFTs like STAR have three types of parities, horizontal, diagonal and anti-diagonal parities. In the code segmentation step, the horizontal parities are separated from other two parities.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the structure for the input erasure code.
There are two main structures that distribute important and unimportant data in different ways.
As shown in Figure \ref{fig-framework}, in Even structure, important data occupies 1 block in each node, and in Uneven structure, it occupies 1 data stripe.
We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.

Since Even structure distributes important data across each node, it guarantees a more balanced load. Uneven structure concentrates important data into a stripe, and provides greater reliability for important data. A detailed analysis of this will be presented in Section \ref{ReconstructionFT}.

\subsubsection{Code Generation}\label{code-gen}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and Structure.

We define the naming rules of the output Approximate Code as \textbf{APPR.CodeName} ($k,r,g,h$,Structure), where ``CodeName'' is the name of the input erasure code. Paremeter $Structure$ is Even or Uneven and it can be omitted when not focusing on the specific construction.

In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ stripes, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes $N$ in Approximate Code ($k,r,g,h$) is 
$N= h*(k+r) + g$.

Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually 1 or 2.

\subsection{\textcolor{red}{Approximate RS Code}}
For RS($k,p$), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$. RS also supports both two structures.

For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS($4,3$). It is divided into two local parities and one global parities with the Uneven structure and it generate Approximate RS Code ($4,2,1,3$,Uneven).
As a result, the unimportant data constitutes RS($4,2$), and the important data constitutes RS($4,3$).

\subsection{Approximate XOR-based Codes}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS. This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP Code.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{photo/AP-5214-v2.pdf}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

\iffalse
\begin{figure}[ht]
\includegraphics[width =0.8\linewidth]{photo/EVENODD-STAR-v2.pdf}
\caption{Encoding process of APPR.STAR($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}\label{fig-star}
\end{figure}
\fi
